Naturalness in U(1) extensions of the MSSM

### 2014-11-13 paper/e6ssm-tuning-paper.tex
Starting to add approximate RGE solutions for U(1) model

q(Q)=q(M_X)+\int_0^t q(t')\;\textrm{d}t'\approx q(M_X)+\frac{t}{16\pi^2}\left ( \beta_q^{(1)}+\frac{\beta_q^{(2)}}{16\pi^2}\right )+\frac{t^2}{(16\pi^2)^2}b_q^{(2)}(M_X),

@@

\begin{subequations}\label{eq:mubetas}

@@

\beta_\mu^{(1)}&=\mu\left ( 3y_t^2+3y_b^2+y_\tau^2-3g_2^2-\frac{3}{5}g_1^2\right ),\label{eq:mubeta1}\\

@@

&\qquad{}+\frac{6}{5}g_1^2y_\tau^2+\frac{15}{2}g_2^4+\frac{9}{5}g_1^2g_2^2+\frac{207}{50}g_1^4\bigg ),\label{eq:mubeta2}\\

@@

&\quad{}-12g_2^2(3y_t^2+3y_b^2+y_\tau^2)-\frac{4}{5}g_1^2(11y_t^2+8y_b^2+6y_\tau^2)+3g_2^4-\frac{189}{25}g_1^4+\frac{18}{5}g_1^2g_2^2\Bigg ].\label{eq:mub2}

@@

\begin{subequations}\label{eq:Bbetas}

@@

\beta_B^{(1)}&=6y_t^2A_t+6y_b^2A_b+2y_\tau^2A_\tau+6g_2^2M_2+\frac{6}{5}g_1^2M_1,\label{eq:Bbeta1}\\

@@

&\quad{}-30g_2^4M_2-\frac{18}{5}g_1^2g_2^2(M_1+M_2)-\frac{414}{25}g_1^4M_1,\label{eq:Bbeta2}\\

@@

&\quad{}+12g_2^4M_2+\frac{396}{25}g_1^4M_1.\label{eq:Bb2}

@@

\begin{subequations}\label{eq:mHd2Betas}

@@

&\quad{}-6g_2^2M_2^2-\frac{3}{5}g_1^2\left ( \mathcal{S}+2M_1^2\right ),\label{eq:mHd2beta1}\\

@@

&\quad{}+\frac{1}{25}g_1^4\left ( 621M_1^2+18m_{H_d}^2+\sum_{i=1}^3[18m_{Li}^2+2m_{Qi}^2+56m_{ui}^2+2m_{di}^2-18m_{ei}^2]\right ),\label{eq:mHd2beta2}\\

@@

&\quad{}-18g_2^4M_2^2-\frac{198}{25}g_1^4\left ( \mathcal{S}+3M_1^2\right ),\label{eq:mHd2b2}

@@

\begin{subequations}\label{eq:mHu2Betas}

@@

\beta_{m_{H_u}^2}^{(1)}&=6y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+A_t^2\right )-6g_2^2M_2^2+\frac{3}{5}g_1^2\left ( \mathcal{S}-2M_1^2\right ),\label{eq:mHu2beta1}\\

@@

&\quad{}+\frac{1}{25}g_1^4\left ( 621M_1^2+18m_{H_u}^2+\sum_{i=1}^3[4m_{Qi}^2-8m_{ui}^2+10m_{di}^2+54m_{ei}^2]\right ),\label{eq:mHu2beta2}\\

@@

&\quad{}+\frac{198}{25}g_1^4\left ( \mathcal{S}-3M_1^2\right )-18g_2^4M_2^2.\label{eq:mHu2b2}

@@

\begin{equation}\label{eq:gaugeBetaContribution}

@@

\begin{subequations}\label{eq:mq32Betas}

@@

&\quad{}-\frac{32}{3}g_3^2M_3^2-6g_2^2M_2^2+\frac{1}{5}g_1^2\left ( \mathcal{S}-\frac{2}{3}M_1^2\right ),\label{eq:mQ32beta1}\\

@@

&\qquad\qquad\qquad{}+\sum_{i=1}^3\left [ 2m_{Qi}^2-6m_{Li}^2-24m_{ui}^2+6m_{di}^2+42m_{ei}^2\right ]\bigg ),\label{eq:mQ32beta2}\\

@@

&\quad{}+96g_3^4M_3^2-18g_2^4M_2^2+\frac{66}{25}g_1^4(\mathcal{S}-M_1^2),\label{eq:mQ32b2}

@@

\begin{subequations} \label{eq:mu32Betas}

@@

\beta_{m_{u3}^2}^{(1)}&=4y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+A_t^2\right )-\frac{32}{3}g_3^2M_3^2-\frac{4}{5}g_1^2\left ( \mathcal{S}+\frac{8}{3}M_1^2\right ),\label{eq:mu32beta1}\\

@@

&\quad{}+\frac{4}{75}g_1^4\left ( 856M_1^2+3m_{H_u}^2+21m_{H_d}^2+\sum_{i=1}^3\left [ 3m_{Qi}^2+21m_{Li}^2+64m_{ui}^2+4m_{di}^2-12m_{ei}^2\right ]\right ),\label{eq:mu32beta2}\\

@@

&\quad{}+96g_3^4M_3^2-\frac{264}{25}g_1^4\left ( \mathcal{S}+4M_1^2\right ).\label{eq:mu32b2}

@@

\begin{subequations}\label{eq:AtBetas}

@@

\beta_{A_t}^{(1)}&=12y_t^2A_t+2y_b^2A_b+\frac{32}{3}g_3^2M_3+6g_2^2M_2+\frac{26}{15}g_1^2M_1,\label{eq:Atbeta1}\\

@@

&\quad{}-2g_2^2g_1^2(M_1+M_2)-\frac{5486}{225}g_1^4M_1,\label{eq:Atbeta2}\\

@@

&\quad{}-64g_3^4M_3+12g_2^4M_2+\frac{572}{25}g_1^4M_1.\label{eq:Atb2}

@@

In $U(1)$ extended models the 2-loop RGEs are lengthy even if $U(1)$ mixing effects are

@@

second generation Yukawas are zero along with the soft SUSY breaking trilinears.

% NB before submission replace this with a copy-paste of the bbl file?
\bibliography{bibliography}{}
\end{document}

>>>>

q(Q)=q(M_X)+\frac{t}{16\pi^2}\left ( \beta_q^{(1)}+\frac{\beta_q^{(2)}}{16\pi^2}\right )+\frac{t^2}{(16\pi^2)^2}b_q^{(2)}(M_X),

@@

\begin{subequations}\label{eq:MSSMmubetas}

@@

\beta_\mu^{(1)}&=\mu\left ( 3y_t^2+3y_b^2+y_\tau^2-3g_2^2-\frac{3}{5}g_1^2\right ),\label{eq:MSSMmubeta1}\\

@@

&\qquad{}+\frac{6}{5}g_1^2y_\tau^2+\frac{15}{2}g_2^4+\frac{9}{5}g_1^2g_2^2+\frac{207}{50}g_1^4\bigg ),\label{eq:MSSMmubeta2}\\

@@

&\quad{}-12g_2^2(3y_t^2+3y_b^2+y_\tau^2)-\frac{4}{5}g_1^2(11y_t^2+8y_b^2+6y_\tau^2)+3g_2^4-\frac{189}{25}g_1^4+\frac{18}{5}g_1^2g_2^2\Bigg ].\label{eq:MSSMmub2}

@@

\begin{subequations}\label{eq:MSSMBbetas}

@@

\beta_B^{(1)}&=6y_t^2A_t+6y_b^2A_b+2y_\tau^2A_\tau+6g_2^2M_2+\frac{6}{5}g_1^2M_1,\label{eq:MSSMBbeta1}\\

@@

&\quad{}-30g_2^4M_2-\frac{18}{5}g_1^2g_2^2(M_1+M_2)-\frac{414}{25}g_1^4M_1,\label{eq:MSSMBbeta2}\\

@@

&\quad{}+12g_2^4M_2+\frac{396}{25}g_1^4M_1.\label{eq:MSSMBb2}

@@

\begin{subequations}\label{eq:MSSMmHd2Betas}

@@

&\quad{}-6g_2^2M_2^2-\frac{3}{5}g_1^2\left ( \mathcal{S}+2M_1^2\right ),\label{eq:MSSMmHd2beta1}\\

@@

&\quad{}+\frac{1}{25}g_1^4\left ( 621M_1^2+18m_{H_d}^2+\sum_{i=1}^3[18m_{Li}^2+2m_{Qi}^2+56m_{ui}^2+2m_{di}^2-18m_{ei}^2]\right ),\label{eq:MSSMmHd2beta2}\\

@@

&\quad{}-18g_2^4M_2^2-\frac{198}{25}g_1^4\left ( \mathcal{S}+3M_1^2\right ),\label{eq:MSSMmHd2b2}

@@

\begin{subequations}\label{eq:MSSMmHu2Betas}

@@

\beta_{m_{H_u}^2}^{(1)}&=6y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+A_t^2\right )-6g_2^2M_2^2+\frac{3}{5}g_1^2\left ( \mathcal{S}-2M_1^2\right ),\label{eq:MSSMmHu2beta1}\\

@@

&\quad{}+\frac{1}{25}g_1^4\left ( 621M_1^2+18m_{H_u}^2+\sum_{i=1}^3[4m_{Qi}^2-8m_{ui}^2+10m_{di}^2+54m_{ei}^2]\right ),\label{eq:MSSMmHu2beta2}\\

@@

&\quad{}+\frac{198}{25}g_1^4\left ( \mathcal{S}-3M_1^2\right )-18g_2^4M_2^2.\label{eq:MSSMmHu2b2}

@@

\begin{equation}\label{eq:MSSMgaugeBetaContribution}

@@

\begin{subequations}\label{eq:MSSMmq32Betas}

@@

&\quad{}-\frac{32}{3}g_3^2M_3^2-6g_2^2M_2^2+\frac{1}{5}g_1^2\left ( \mathcal{S}-\frac{2}{3}M_1^2\right ),\label{eq:MSSMmQ32beta1}\\

@@

&\qquad\qquad\qquad{}+\sum_{i=1}^3\left [ 2m_{Qi}^2-6m_{Li}^2-24m_{ui}^2+6m_{di}^2+42m_{ei}^2\right ]\bigg ),\label{eq:MSSMmQ32beta2}\\

@@

&\quad{}+96g_3^4M_3^2-18g_2^4M_2^2+\frac{66}{25}g_1^4(\mathcal{S}-M_1^2),\label{eq:MSSMmQ32b2}

@@

\begin{subequations} \label{eq:MSSMmu32Betas}

@@

\beta_{m_{u3}^2}^{(1)}&=4y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+A_t^2\right )-\frac{32}{3}g_3^2M_3^2-\frac{4}{5}g_1^2\left ( \mathcal{S}+\frac{8}{3}M_1^2\right ),\label{eq:MSSMmu32beta1}\\

@@

&\quad{}+\frac{4}{75}g_1^4\left ( 856M_1^2+3m_{H_u}^2+21m_{H_d}^2+\sum_{i=1}^3\left [ 3m_{Qi}^2+21m_{Li}^2+64m_{ui}^2+4m_{di}^2-12m_{ei}^2\right ]\right ),\label{eq:MSSMmu32beta2}\\

@@

&\quad{}+96g_3^4M_3^2-\frac{264}{25}g_1^4\left ( \mathcal{S}+4M_1^2\right ).\label{eq:MSSMmu32b2}

@@

\begin{subequations}\label{eq:MSSMAtBetas}

@@

\beta_{A_t}^{(1)}&=12y_t^2A_t+2y_b^2A_b+\frac{32}{3}g_3^2M_3+6g_2^2M_2+\frac{26}{15}g_1^2M_1,\label{eq:MSSMAtbeta1}\\

@@

&\quad{}-2g_2^2g_1^2(M_1+M_2)-\frac{5486}{225}g_1^4M_1,\label{eq:MSSMAtbeta2}\\

@@

&\quad{}-64g_3^4M_3+12g_2^4M_2+\frac{572}{25}g_1^4M_1.\label{eq:MSSMAtb2}

@@

In $U(1)$ extended models the 2-loop RGEs are somewhat more lengthy even if $U(1)$ mixing effects are

@@

second generation Yukawas are zero along with the soft SUSY breaking trilinears. At tree level in the EWSB conditions
the parameters that must be expanded are $\lambda$, $A_\lambda$, $m_{H_u}^2$, $m_{H_d}^2$, $m_S^2$ and $g_1$, $g_2$ and $g_1'$.
The coefficients in the expansion of $\lambda$ may be written
\begin{subequations}\label{eq:USSMLambdaBetas}
\beta_{\lambda}^{(1)}&=\lambda\Big (2\lambda^2+2\Sigma_\lambda +3\Sigma_\kappa+ 3y_t^2 + 3y_b^2 + y_\tau^2-\frac{3}{5}g_1^2-3g_2^2-2g_1'^2\left (\tilde{Q}_1^2+\tilde{Q}_2^2+\tilde{Q}_S^2\right )\Big ), \label{eq:USSMLambdabeta1}
\beta_{\lambda}^{(2)}&=\lambda
\Sigma_\lambda=\lambda_1^2+\lambda_2^2+\lambda_3^2,\qquad \Sigma_\kappa=\kappa_1^2+\kappa_2^2+\kappa_3^2.
% NB before submission replace this with a copy-paste of the bbl file?
\bibliography{bibliography}{}
\end{document}
